My title

### 2023-03-16 outputs/paper/Happiness in America: A Comprehensive Analysis of the Effects of Demographic Factors.qmd
graph new changes

fig1 <- ggplot(happiness_data, aes(x = Year, y = People, fill = Happy)) +
  geom_line(aes(group = Happy, color = Happy), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       color = "Happy level")
fig1 <- fig1  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 12,
             x = 0.5,
             y = 1.05)
fig1
```

@@

# Only for white
white_data <- filter(race_data, Race == "White")
gwhite <- ggplot(white_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "White people",
           color = "Happy level")

# Only for black
black_data <- filter(race_data, Race == "Black")
gblack <- ggplot(black_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip()+
      labs(y = "Year", x = "Percentages", fill = "Happy Level", 
           title = "black people",
           color = "Happy level")

# Only for others
others_data <- filter(race_data, Race == "Others")
gothers <- ggplot(others_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "other race",
           color = "Happy level")

@@

# graph for less than high school
less_high_school_data <- filter(degree_data, Degree == "Less than high school")
glesshighschool <- ggplot(less_high_school_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Less than high school",
           color = "Happy level")

# graph for high school
high_school_data <- filter(degree_data, Degree == "High school")
ghighschool <- ggplot(high_school_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "High school",
           color = "Happy level")

# graph for associate/junior college
junior_data <- filter(degree_data, Degree == "Associate/junior college")
gjunior <- ggplot(junior_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Associate/junior college",
           color = "Happy level")

# graph for bachelor
bachelor_data <- filter(degree_data, Degree == "Bachelor's")
gbachelor <- ggplot(bachelor_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Bachelor",
           color = "Happy level")

# graph for graduate
graduate_data <- filter(degree_data, Degree == "Graduate")
graduate<- ggplot(graduate_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Graduate",
           color = "Happy level")

@@

# graph for self-employee
self_data <- filter(employee_status_data, Employee_status == "Self-employed")
gself<- ggplot(self_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Self-employed",
           color = "Happy level")

# graph for someone else
someone_data <- filter(employee_status_data, Employee_status == "Someone else")
gsomeone <- ggplot(someone_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Someone else",
           color = "Happy level")

@@

# graph for married
married_data <- filter(marital_status_data, Marital_status == "Married")
gmarried_data <- ggplot(married_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Married",
           color = "Happy level")

# graph for widowed
widowed_data <- filter(marital_status_data, Marital_status == "Widowed")
gwidowed_data <- ggplot(widowed_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Widowed",
           color = "Happy level")

# graph for divorced
divorced_data <- filter(marital_status_data, Marital_status == "Divorced")
gdivorced_data <- ggplot(divorced_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Divorced",
           color = "Happy level")

# graph for separated
separated_data <- filter(marital_status_data, Marital_status == "Separated")
gseparated_data <- ggplot(separated_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Separated",
           color = "Happy level")

# graph for never married
never_married_data <- filter(marital_status_data, Marital_status == "Never married")
gnever_married<- ggplot(never_married_data, 
             aes(y = Year, 
                 fill = Happy)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Never married",
           color = "Happy level")

>>>>

fig1 <- ggplot(happiness_data, aes(x = Year, y = People, fill = Happy_level)) +
  geom_line(aes(group = Happy_level, color = Happy_level), size = 1.2) +
  scale_fill_manual(values = happy_colors) +
  scale_color_manual(values = happy_colors) +
  labs(x = "Year", y = "Number of Respondents", fill = "Happy Level", 
       color = "Happy level")
fig1 <- fig1  +
  draw_label("Trends in happiness levels for different genders from 1972 to 2021", 
             fontface = "bold", 
             size = 12,
             x = 0.5,
             y = 1.05)
fig1
```

@@

# Only for white
white_data <- filter(race_data, Race == "White")
gwhite <- ggplot(white_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "White people",
           color = "Happy level")

# Only for black
black_data <- filter(race_data, Race == "Black")
gblack <- ggplot(black_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip()+
      labs(y = "Year", x = "Percentages", fill = "Happy Level", 
           title = "black people",
           color = "Happy level")

# Only for others
others_data <- filter(race_data, Race == "Others")
gothers <- ggplot(others_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "other race",
           color = "Happy level")

@@

# graph for less than high school
less_high_school_data <- filter(degree_data, Degree == "Less than high school")
glesshighschool <- ggplot(less_high_school_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Less than high school",
           color = "Happy level")

# graph for high school
high_school_data <- filter(degree_data, Degree == "High school")
ghighschool <- ggplot(high_school_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "High school",
           color = "Happy level")

# graph for associate/junior college
junior_data <- filter(degree_data, Degree == "Associate/junior college")
gjunior <- ggplot(junior_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Associate/junior college",
           color = "Happy level")

# graph for bachelor
bachelor_data <- filter(degree_data, Degree == "Bachelor's")
gbachelor <- ggplot(bachelor_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Bachelor",
           color = "Happy level")

# graph for graduate
graduate_data <- filter(degree_data, Degree == "Graduate")
graduate<- ggplot(graduate_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Graduate",
           color = "Happy level")

@@

# graph for self-employee
self_data <- filter(employee_status_data, Employee_status == "Self-employed")
gself<- ggplot(self_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Self-employed",
           color = "Happy level")

# graph for someone else
someone_data <- filter(employee_status_data, Employee_status == "Someone else")
gsomeone <- ggplot(someone_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Someone else",
           color = "Happy level")

@@

# graph for married
married_data <- filter(marital_status_data, Marital_status == "Married")
gmarried_data <- ggplot(married_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Married",
           color = "Happy level")

# graph for widowed
widowed_data <- filter(marital_status_data, Marital_status == "Widowed")
gwidowed_data <- ggplot(widowed_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Widowed",
           color = "Happy level")

# graph for divorced
divorced_data <- filter(marital_status_data, Marital_status == "Divorced")
gdivorced_data <- ggplot(divorced_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Divorced",
           color = "Happy level")

# graph for separated
separated_data <- filter(marital_status_data, Marital_status == "Separated")
gseparated_data <- ggplot(separated_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Separated",
           color = "Happy level")

# graph for never married
never_married_data <- filter(marital_status_data, Marital_status == "Never married")
gnever_married<- ggplot(never_married_data, 
             aes(y = Year, 
                 fill = Happy_level)) + 
      geom_bar(position = "fill") + 
      theme_classic() +
      coord_flip() +
      labs(y = "Year", x = "Percentage", fill = "Happy Level", 
           title = "Never married",
           color = "Happy level")
